---
title: "Aquatic Invertebrates"
output: html_document
date: "2023-11-30"
---


```{r setup, include=FALSE}

install.packages("ggplot2")
install.packages("ggpubr")
install.packages("dplyr")
install.packages("cowplot")
library(ggplot2)
library(ggpubr)
library(dplyr)
library(cowplot)

#Creating a Plot that compares the taxonomic richness of Aquatic Invertebrates Between North and Southern Plot

#Creating data frames that only by sampling site

N.stream.inverts<- Aquatic_Invertebrates[1:24, ] #extracting samples from the northern stream
N.stream.inverts<-cbind(N.stream.inverts, 
                        Location=c("North Stream"))
#creating a new column in the data frame by location to indicate the samples came from the north stream


S.stream.inverts<-Aquatic_Invertebrates[25:36,]#extracting samples from the southern stream
S.stream.inverts<-cbind(S.stream.inverts, 
                        Location=c("South Stream"))
#creating a new column in the data frame by location to indicate the samples came from the south stream

S.marsh.inverts<-Aquatic_Invertebrates[37:49, ] #extracting samples from the marsh in the southern plot
S.marsh.inverts<-cbind(S.marsh.inverts, 
                        Location=c("Marsh"))
#creating a new column in the data frame by location to indicate the samples came from the south marsh

a.inverts<-rbind(N.stream.inverts, 
                 S.stream.inverts, 
                 S.marsh.inverts)

plot_transects1 <- ggplot(N.stream.inverts, aes(x =reorder(order, organismQuantity), y = organismQuantity, fill = "North Stream")) +
  geom_bar(stat = "identity") +
  labs(x = NULL, y= NULL, title = 'North Stream') +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5, size = 5),
        plot.title = element_text(color = "purple")) +  # Set title color to red
  scale_fill_manual(values = "purple")  # Set fill color to red

plot_transects1

plot_transects2 <- ggplot(S.stream.inverts, aes(x =reorder(order, organismQuantity), y = organismQuantity, fill = "South Stream")) +
  geom_bar(stat = "identity") +
  labs(x = NULL, y='Organism Count', title = 'South Stream') +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5, size = 5),
        plot.title = element_text(color = "blue")) +  # Set title color to green
  scale_fill_manual(values = "blue")  # Set fill color to green

plot_transects3 <- ggplot(S.marsh.inverts, aes(x =reorder(order, organismQuantity), y = organismQuantity, fill = "Marsh")) +
  geom_bar(stat = "identity") +
  labs(x = 'Order', y=NULL, title = 'Lower') +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5, size = 5),
        plot.title = element_text(color = "green")) +  # Set title color to blue
  scale_fill_manual(values = "green")  # Set fill color to blue

# Use plot_grid to arrange the plots vertically
A.plot.transects<-plot_grid(
  plot_transects1, plot_transects2, plot_transects3, ncol = 1)

A.plot.transects


  


```

```
```{r setup, include=FALSE}
##Water Quality##


N.stream.index<-c(4,5,8,10,9,4,5,4,5,8,10,4,5,8)
#in order to calculate the water quality index for the North Stream, I added up all the scores from the BMWP scores associated with the unique invertebrate family present in our dataset and got the mean. 

mean(N.stream.index) 
#6.35

S.stream.inverts$family
S.stream.inverts$order
S.stream.index<-c(5, 10, 5, 5, )
mean(S.stream.index) 
#7.5
#in order to calculate the water quality index for the South Stream, I added up all the scores from the BMWP scores associated with the unique invertebrate family present in our dataset and got the mean.

unique(S.marsh.inverts$order)
S.marsh.index<-c(5,5,1,10)
mean(S.marsh.index) 
#5.25
#in order to calculate the water quality index for the South Marsh, I added up all the scores from the BMWP scores associated with the unique invertebrate family present in our dataset and got the mean.

```

